---
title: "GLS HW3"
author: "宋倩 统计系 15420161152176"
date: "2017/10/14"
output:
  word_document: default
  html_document: default
---
###4.1  
(a)
```{r}
y <- c(1,6,16,23,27,39,31,30,43,51,63,70,
       88,97,91,104,110,113,149,159)
i <- 1:20
plot(i,y)
```
(b)
```{r}
plot(log(i),log(y))
```
The plot of log(y) against log(i) is approximately linear with a non-zero intercept.
  
  (c)
Since $g(\lambda_i)=log(\lambda_i)=\beta_1+\beta_2x_i=\eta_i$,  
then   
$\frac{\partial \lambda_i}{\partial \eta_i}=e^{\eta_i}$,  
$w_{ii}=\frac{1}{var(Y_i)}\lambda_i^2=\lambda_i=e^{{x_i}^T\beta}$  
and from (4.24) we can get  
$z_i=x_i^T\beta+\frac{y_i}{\lambda_i}-1$  
```{r}
n=length(y)
b0 <- c(1,1)
loglike<-function(x,y,b0){
     X=cbind(rep(1,n),x)   
     mu=exp(X%*%b0)
	 ll=sum(y*log(mu)-mu)         
	 return(ll)
}
diff <- 1                       
iter <- 0                        
epsi <- 1e-10                     
maxit=1000
while(diff>epsi & iter<maxit)  {
	     ll.old <- loglike(log(i),y,b0)
		 X=cbind(rep(1,n),log(i))
		 mu=exp(X%*%b0)
		 W=diag(as.vector(mu)) 
		 Z=as.vector((y-mu)/mu+log(mu))                                   
		 b1=as.vector(solve(t(X)%*%W%*%X,t(X)%*%W%*%Z))
		 print(b1)
		 ll.new <- loglike(log(i),y,b1)
		 diff <- abs((ll.new-ll.old)/ll.old)
		 iter <- iter+1
		 b0 <- b1
 }
if (iter==maxit) {cat("Warning! May Not Convergence", "\n")}
cat("Number of iterations=",iter,"\n")

X=cbind(rep(1,n),log(i))                   # design matrix
W=diag(as.vector(mu))             # diagonal weight matrix
I=t(X)%*%W%*%X                         # information matrix
myglm=glm(y~log(i),family=poisson)
summary(myglm)

```
(d)The passion regression model is $$y=0.996+1.326log(i)$$  
The parameters are the same as the results of NR.

###4.2  
(a)
```{r}
y <- c(65,156,100,134,16,108,121,4,39,143,56,26,22,1,1,5,65)
x <- c(3.36,2.88,3.63,3.41,3.78,4.02,4.00,4.23,3.73,3.85,3.97,4.51,4.54,5.00,5.00,4.72,5.00)
plot(x,y)
```
y decreases,approximately exponentially,as x increases.  
(b)$g(\mu_i)=log(\mu_i)=\beta_1+\beta_2x_i$  
(c)Since the probability distribution is a special case of Gamma 
$$f(y,\alpha,\beta)=\frac{\beta^\alpha}{\Gamma(\alpha)}y^{\alpha-1}e^{-\beta y}$$
where $\alpha=1,\beta=\theta$,so $$E(Y)=\frac{\alpha}{\beta}=\frac{1}{\theta}$$
$$var(Y)=\frac{\alpha}{\beta^2}=\frac{1}{\theta^2}$$
(d)
```{r}
myglm=glm(y~x,family=Gamma(link = "log"))
summary(myglm)
```
Fitted model is$log(y)=8.4775-1.1093x$  
(e)
```{r}
r <- (y-fitted(myglm))/fitted(myglm)
r
```
The model fits the data well. The standardized residuals are small,except for the last observation which has r=2.467.